# Chapter 2: Regression models and validation


#**Here is my git: <https://github.com/nosape/IODS-project>**


# 1. 
## Description of the dataset
#This dataset consist of studying habits of students. All rows with 'points' value = 0 have been deleted. There are no missing values. It was collected originally in Finnish. 

#In this chunk I import the dataset to R and check the quality: 

#The dataset has 166 observations of 7 variables.4 of the variables are numeric averages with values between 1 and 5.2 variables are integers with values roughly between 15 an 60. 1 variable is factor type, describing the sex of the participants (Male=M;Female=F).
```{r}
students2014 <- read.table("http://s3.amazonaws.com/assets.datacamp.com/production/course_2218/datasets/learning2014.txt", sep=",", header=TRUE)

dim(students2014)
str(students2014)

```

# 2.

#In This chunk I show a graphical overview of the data and show summaries of the variables in the data.

```{r}
library(dplyr)
library(ggplot2)
library(GGally)

#pairs(students2014[-1], col=students2014$gender)

overview <- ggpairs(students2014, mapping = aes(col = gender, alpha = 0.3), lower = list(combo = wrap("facethist", bins = 20)))

overview

```


# 3. 

#In this Chunk create my own model with point as dependent variable and **attitude**, **deep** and **stra** as explanatory variables.

```{r}
stud_model <- lm(points ~ attitude + deep + stra, data = students2014)
stud_model

summary(stud_model)

stud_model2 <-lm(points ~ attitude, data=students2014)
stud_model2

summary(stud_model2)
```
#**Model seems now great with low p-value! I will accept it.**

# 4.
#Interpretation of the summary of **stud_model2** shows that it has multiple r-square of 0.1906 which is roughly similar as Adjusted R-squared of 0.1856. Number is relatively low. **BUT** as one might know we are expecting to see lower that 0.50 r-squared values in behavioral sciences. This means we can dealt with this. 

# 5. 

#Here I show that the model I made:
#A) **has 3 distinguishing values in the residuals vs fitted Values plot. Other than that the model seems good.**.B) **fits the normality assumption because the dots seem to be fit reasonably to the line in the QQ-Plot**.C) **does not have too many high-leverage observations that affect the model. There are no single observations pointing out in the Residuals vs Leverage plot**.
```{r}
plot(stud_model2, which=c(1,2,5))
```
